---
title: "EV DATASET"
author: "Kenrick"
date: "2023-09-18"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

```{r}
# Set a working directory
setwd("/Users/tangangkenrickakere/Desktop/Datasets")

```

# Questions for EV Project.

##1. What regions in the world have the highest EV vehicle sales in the world? 

```{r}
# Load the data
ev_data <- read.csv("IEA-EV-dataEV stockHistoricalCars.csv")
```

```{r}
# Get the total EV sales for each region
counts_region <- table(ev_data$region)
print(counts_region)
```

```{r}
# Convert counts_country to a data frame to be able to create a visualization
counts_region_df <- as.data.frame(counts_region)
names(counts_region_df) <- c("region", "total_count")
```

```{r}
# Create a bar plot using ggplot2
ggplot(counts_region_df, aes(x = region, y = total_count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  labs(x = "region", y = "total_count", title = "Total Count of Each Region") +
  theme_minimal()
```
```{r}
# Sort the data frame by total_count in descending order and select top 5 rows
top_countries <- head(counts_region_df[order(-counts_region_df$total_count), ], 10)
```

```{r}
# Create a bar plot for the top 10 countries
ggplot(top_countries, aes(x = reorder(region, -total_count), y = total_count)) +
  geom_bar(stat = "identity", fill = "red") +
  labs(x = "Region", y = "Total Count", title = "Top 10 Regions by Total Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  # Rotate x-axis labels for better visibility


```


```{r}
#Count the type of electric vehicles in the dataset
counts_powertrain <- table(ev_data$powertrain)
print(counts_powertrain)
```

```{r}
# Select the top 10 regions with the highest EV population
top_10_regions <- ev_population_sorted[1:10]
```

How many EVSE chargers are in the metropolitan areas? 
What amount of EVSE chargers are going to be needed to satisfy the current EV vehicle population? 
What is the total EV vehicle population in Maryland? 
What does the growth in the population of both EV and Plug-in Vehicles from 2020 to 2023 across all the counties in Maryland look like? 
What is the percentage growth in Montgomery County alone?  
Calculate the current growth rate. 
Produce a prediction model to see the expected EV population by 2035. 
 














