---
title: "EV DATASET"
author: "Kenrick"
date: "2023-09-18"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
# Set a working directory
setwd("/Users/tangangkenrickakere/Desktop/Datasets")

```

# Questions for EV Project.

##1. What regions in the world have the highest EV vehicle sales in the world? 

```{r}
# Load the data
ev_data <- read.csv("IEA-EV-dataEV stockHistoricalCars.csv")
```

```{r}
# Group the EV data by region
ev_data_grouped <- group_by(ev_data, region)
```

```{r}
# Get the total EV sales for each region
region_sales <- ev_data %>%
  group_by(region) %>%
  summarise(ev_sales = sum(BEV + PHEV))
```
```{r}
ev_data <- ev_data %>%
  mutate(BEV = EV_stock_Cars + EV_sales_Cars)
```

```{r}
# Select the top 10 regions with the highest EV population
top_10_regions <- ev_population_sorted[1:10]
```

How many EVSE chargers are in the metropolitan areas? 
What amount of EVSE chargers are going to be needed to satisfy the current EV vehicle population? 
What is the total EV vehicle population in Maryland? 
What does the growth in the population of both EV and Plug-in Vehicles from 2020 to 2023 across all the counties in Maryland look like? 
What is the percentage growth in Montgomery County alone?  
Calculate the current growth rate. 
Produce a prediction model to see the expected EV population by 2035. 
 














